Predictors of frog survival following translocations - analyses

### 2022-11-09 code/maps.qmd
Minor code edits

### Create dataset of sample collection points
```{r}
exome_sites <- read_csv(here::here("data", "maps", "exome_sample_sites.csv"))
```
#### Connect to database

@@

```{r}
exome_points_map <- tm_shape(hillshade_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(nps_boundaries) + 
  tm_borders(col = "black") +
  tm_shape(exome_points) + 
  tm_symbols(size = 0.5, 
             col = "bd_status", 
             palette = c("#FFEC8B", "#87CEFA"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Bd status") +
  tm_layout(legend.position = c("right", "top")) +
  tm_compass(type = "4star",
             position = c("left", "bottom"),
             size = 2) +
  tm_scale_bar(breaks = c(0, 25, 50), 
               text.size = 0.7, 
               position = c("left", "bottom"))

@@

### Save map
```{r}
tmap_save(exome_points_map, here::here("out", "map_exome_points.png"))
```

>>>>

### Create dataset of sample collection points

```{r}
exome_sites <- read_csv(here::here("data", "maps", "exome_sample_sites.csv"))
```

#### Connect to database

@@

```{r}
exome_points_map <- tm_shape(hillshade_crop) + 
  tm_rgb(r = 1, g = 2, b = 3) +
  tm_shape(nps_boundaries) + 
  tm_borders(col = "black") +
  tm_shape(exome_points) + 
  tm_symbols(size = 0.5, # increase point size, use darker blue
             col = "bd_status", 
             palette = c("#FFEC8B", "#87CEFA"), # tmap only recognizes basic color names (e.g., "blue" but not "lightblue") - use HEX instead
             title.col = "Bd status") +
  tm_layout(legend.position = c("right", "top")) +
  tm_compass(type = "4star",
             position = c("left", "bottom"),
             size = 2) +
  tm_scale_bar(breaks = c(0, 25, 50), 
               text.size = 0.7, 
               position = c("left", "bottom"))

@@

### Save map

```{r}
tmap_save(exome_points_map, here::here("out", "map_exome_points.png"))
```

### 2022-11-09 code/translocation_survival_analysis.Rmd
Minor code edits

```{r}
tidy(m1d, conf.int = TRUE, conf.level = 0.90)

mcmc_areas(m1d, area_method = "equal height", prob = 0.90, pars = b1) +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", lwd = 0.5) +  
  ggtitle("Model with standardized predictors & translocation_id as grouping variable",
          "Posterior distributions with medians & 90% uncertainty intervals")

>>>>

```{r}
tidy(m1d, conf.int = TRUE, conf.level = 0.95)

mcmc_areas(m1d, area_method = "equal height", prob = 0.95, pars = b1) +
  geom_vline(xintercept = 0, color = "red", linetype = "dashed", lwd = 0.5) +  
  ggtitle("Model with standardized predictors & translocation_id as grouping variable",
          "Posterior distributions with medians & 95% uncertainty intervals")
